---
title: "Homework 6"
output: github_document
---
```{r setup, include = FALSE}
library(tidyverse)
library(purrr)
library(rvest)
library(dplyr)
library(stringr)
library(modelr)
library(p8105.datasets)


knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```



## Problem 1

load in the data
```{r}
homicide_df = 
  read_csv("homicide-data.csv", na = c("", "NA", "Unknown")) %>% 
  mutate(
    city_state = str_c(city, state, sep = ", "),
    victim_age = as.numeric(victim_age),
    resolution = case_when(
      disposition == "Closed without arrest" ~ 0,
      disposition == "Open/No arrest"        ~ 0,
      disposition == "Closed by arrest"      ~ 1)
    ) %>% 
  filter(
    victim_race %in% c("White", "Black"),
    city_state != "Tulsa, AL") %>% 
  select(city_state, resolution, victim_age, victim_race, victim_sex)
  
```

Start with one city.

```{r}
baltimore_df = 
  homicide_df %>% 
  filter(city_state == "Baltimore, MD")

glm(resolution ~ victim_age + victim_race + victim_sex,
    data = baltimore_df,
    family = binomial()) %>% 
  broom::tidy() %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(term, OR, starts_with("CI")) %>% 
  knitr::kable(digits = 3)
```


Try this across cities.

```{r}
models_results_df = 
  homicide_df %>% 
  nest(data = -city_state) %>% 
  mutate(
    models = map(.x = data, ~glm(resolution ~ victim_race + victim_sex, data = .x, family = binomial())),
    results = map(models, broom::tidy)
  ) %>% 
  select(city_state, results) %>% 
  unnest(results) %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(city_state, term, OR, starts_with("CI"))
```

Plot some ORs

```{r}
models_results_df %>% 
  filter(term == "victim_sexMale") %>% 
  mutate(city_state = fct_reorder(city_state, OR)) %>% 
  ggplot(aes(x = city_state, y = OR)) +
  geom_point() +
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
  
```


## Problem 2
build a model - can look thru those variables and select which to put in, come up with a reason as to why you want to put those vars in
could do stepwise model building
compare to one that uses length at birth and gest age as predictors, one that contains head circumference sex etc. 


looking at prediction accuracy based on birthweight for those vars

perhaps start with those two bullet points, look at cross val lecture and adjust code accordingly
take full dataset and figreu out model u want to propose in this context - just start picking vars and fitting htem, looking at results to see if things are significant

big issues with dataset?

```{r}
# baby_df %>% 
#   modelr::add_residuals(model_fit) %>% 
#   ggplot(aes(x = gaweeks, y = resid)) +
#   geom_point()
```


## Problem 3

download dataset, fit model to dataset, make sure can compute adjusted r-sq (comes from broom::glance), broom::tidy, estimated coefficients, rearrange things so have intercept and slope next to each other that you can multiply and take the log of. 



