---
title: "Homework 6"
output: github_document
---
```{r setup, include = FALSE}
library(tidyverse)
library(purrr)
library(rvest)
library(dplyr)
library(stringr)
library(modelr)
library(p8105.datasets)


knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```



## Problem 1

load in the data
```{r}
homicide_df = 
  read_csv("homicide-data.csv", na = c("", "NA", "Unknown")) %>% 
  mutate(
    city_state = str_c(city, state, sep = ", "),
    victim_age = as.numeric(victim_age),
    resolution = case_when(
      disposition == "Closed without arrest" ~ 0,
      disposition == "Open/No arrest"        ~ 0,
      disposition == "Closed by arrest"      ~ 1)
    ) %>% 
  filter(
    victim_race %in% c("White", "Black"),
    city_state != "Tulsa, AL") %>% 
  select(city_state, resolution, victim_age, victim_race, victim_sex)
  
```

Start with one city.

```{r}
baltimore_df = 
  homicide_df %>% 
  filter(city_state == "Baltimore, MD")

glm(resolution ~ victim_age + victim_race + victim_sex,
    data = baltimore_df,
    family = binomial()) %>% 
  broom::tidy() %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(term, OR, starts_with("CI")) %>% 
  knitr::kable(digits = 3)
```


Try this across cities.

```{r}
models_results_df = 
  homicide_df %>% 
  nest(data = -city_state) %>% 
  mutate(
    models = map(.x = data, ~glm(resolution ~ victim_race + victim_sex, data = .x, family = binomial())),
    results = map(models, broom::tidy)
  ) %>% 
  select(city_state, results) %>% 
  unnest(results) %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(city_state, term, OR, starts_with("CI"))
```

Plot some ORs

```{r}
models_results_df %>% 
  filter(term == "victim_sexMale") %>% 
  mutate(city_state = fct_reorder(city_state, OR)) %>% 
  ggplot(aes(x = city_state, y = OR)) +
  geom_point() +
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
  
```


## Problem 2


Importing and tidying data
```{r}
birthweight_df = 
  read_csv("birthweight.csv") %>% 
  mutate(
    frace = recode(frace,
                  `1` = "White",
                  `2` = "Black",
                  `3` = "Asian",
                  `4` = "Puerto Rican",
                  `8` = "Other")
  ) %>% 
  mutate(
    mrace = recode(mrace,
                  `1` = "White",
                  `2` = "Black",
                  `3` = "Asian",
                  `4` = "Puerto Rican",
                  `8` = "Other")
  ) %>% 
  mutate(
    malform = recode(malform,
                          `0` = "absent",
                          `1` = "present")
  ) %>% 
  mutate(
    babysex = recode(babysex,
                     `1` = "male",
                     `2` = "female")
  ) %>% view()


sum(is.na(birthweight_df))
# no missing data points!!

```
Initial thoughts - not a lot of malformations, previous low birthweight babies, or prior small for gestational age babies

Thinking of looking into:

* gestational age (gaweeks) - this seems like it would be a highly predictive var given fetal development (they gain the most weight during the final trimester of gestation)
* blength - a 2012 [study](https://pubmed.ncbi.nlm.nih.gov/22535715/#:~:text=The%20addition%20of%20fetal%20length,%25%20versus%207.5%25%3B%20P%20%3C%20.) by Melamed et al. found that the addition of fetal length as a variable significantly improved their model's correlation with birth weight.
* mrace - also correlated with access to adequate care; Black mothers are more likely to have preterm and low-birthweight infants
* delwt - A 2010 [study](https://www.ncbi.nlm.nih.gov/pmc/articles/PMC2974327/#:~:text=Observational%20studies%20have%20generally%20found,birth%20weight%20or%20infant%20adiposity.&text=Moreover%2C%20maternal%20adiposity%20tends%20to,BMI29%20than%20paternal%20adiposity.) found that maternal weight gain during pregnancy increases infant birthweight


Some exploration to visualize chosen vars
```{r}
birthweight_df %>% 
  ggplot(aes(x = gaweeks, y = bwt)) +
  geom_point()

birthweight_df %>% 
  ggplot(aes(x = blength, y = bwt)) +
  geom_point()

birthweight_df %>% 
  ggplot(aes(x = mrace, y = bwt)) +
  geom_point()

birthweight_df %>% 
  ggplot(aes(x = delwt, y = bwt)) +
  geom_point()
```

Will first make the following models:

* One using length at birth and gestational age as predictors (main effects only)
* One using head circumference, length, sex, and all interactions (including the three-way interaction) between these


Lenght at birth and gestational age as predictors model

```{r}

```










could do stepwise model building
compare to one that uses length at birth and gest age as predictors, one that contains head circumference sex etc. 


looking at prediction accuracy based on birthweight for those vars

perhaps start with those two bullet points, look at cross val lecture and adjust code accordingly
take full dataset and figreu out model u want to propose in this context - just start picking vars and fitting htem, looking at results to see if things are significant

big issues with dataset?

```{r}
# baby_df %>% 
#   modelr::add_residuals(model_fit) %>% 
#   ggplot(aes(x = gaweeks, y = resid)) +
#   geom_point()
```


## Problem 3

download dataset, fit model to dataset, make sure can compute adjusted r-sq (comes from broom::glance), broom::tidy, estimated coefficients, rearrange things so have intercept and slope next to each other that you can multiply and take the log of. 



