---
title: "Homework 6"
output: github_document
---
```{r setup, include = FALSE}
library(tidyverse)
library(purrr)
library(rvest)
library(dplyr)
library(stringr)
library(modelr)
library(p8105.datasets)
library(gam)
library(purrr)


knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```



## Problem 1

load in the data
```{r}
homicide_df = 
  read_csv("homicide-data.csv", na = c("", "NA", "Unknown")) %>% 
  mutate(
    city_state = str_c(city, state, sep = ", "),
    victim_age = as.numeric(victim_age),
    resolution = case_when(
      disposition == "Closed without arrest" ~ 0,
      disposition == "Open/No arrest"        ~ 0,
      disposition == "Closed by arrest"      ~ 1)
    ) %>% 
  filter(
    victim_race %in% c("White", "Black"),
    city_state != "Tulsa, AL") %>% 
  select(city_state, resolution, victim_age, victim_race, victim_sex)
  
```

Start with one city.

```{r}
baltimore_df = 
  homicide_df %>% 
  filter(city_state == "Baltimore, MD")

glm(resolution ~ victim_age + victim_race + victim_sex,
    data = baltimore_df,
    family = binomial()) %>% 
  broom::tidy() %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(term, OR, starts_with("CI")) %>% 
  knitr::kable(digits = 3)
```


Try this across cities.

```{r}
models_results_df = 
  homicide_df %>% 
  nest(data = -city_state) %>% 
  mutate(
    models = map(.x = data, ~glm(resolution ~ victim_race + victim_sex, data = .x, family = binomial())),
    results = map(models, broom::tidy)
  ) %>% 
  select(city_state, results) %>% 
  unnest(results) %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(city_state, term, OR, starts_with("CI"))
```

Plot some ORs

```{r}
models_results_df %>% 
  filter(term == "victim_sexMale") %>% 
  mutate(city_state = fct_reorder(city_state, OR)) %>% 
  ggplot(aes(x = city_state, y = OR)) +
  geom_point() +
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
  
```


## Problem 2


Importing and tidying data
```{r}
birthweight_df = 
  read_csv("birthweight.csv") %>% 
  mutate(
    frace = as.factor(recode(frace,
                  `1` = "White",
                  `2` = "Black",
                  `3` = "Asian",
                  `4` = "Puerto Rican",
                  `8` = "Other"))
  ) %>% 
  mutate(
    mrace = as.factor(recode(mrace,
                  `1` = "White",
                  `2` = "Black",
                  `3` = "Asian",
                  `4` = "Puerto Rican",
                  `8` = "Other"))
  ) %>% 
  mutate(
    malform = as.factor(recode(malform,
                          `0` = "absent",
                          `1` = "present"))
  ) %>% 
  mutate(
    babysex = as.factor(recode(babysex,
                     `1` = "male",
                     `2` = "female"))
  ) %>% view()


sum(is.na(birthweight_df))
# no missing data points!!

```
Initial thoughts - not a lot of malformations, previous low birthweight babies, or prior small for gestational age babies

Thinking of looking into:

* gestational age (gaweeks) - this seems like it would be a highly predictive var given fetal development (they gain the most weight during the final trimester of gestation)
* blength - a 2012 [study](https://pubmed.ncbi.nlm.nih.gov/22535715/#:~:text=The%20addition%20of%20fetal%20length,%25%20versus%207.5%25%3B%20P%20%3C%20.) by Melamed et al. found that the addition of fetal length as a variable significantly improved their model's correlation with birth weight.
* mrace - also correlated with access to adequate care; Black mothers are more likely to have preterm and low-birthweight infants
* delwt - A 2010 [study](https://www.ncbi.nlm.nih.gov/pmc/articles/PMC2974327/#:~:text=Observational%20studies%20have%20generally%20found,birth%20weight%20or%20infant%20adiposity.&text=Moreover%2C%20maternal%20adiposity%20tends%20to,BMI29%20than%20paternal%20adiposity.) found that maternal weight gain during pregnancy increases infant birthweight
* smoken - smoking has deleterious effects on pregnancy, including increasing the risk of preterm births and low birthweight (CDC)
* babysex - male infants typically have higher birthweight than female infants
* ppbmi - pre-pregnancy bmi [is often predictive](https://www.ncbi.nlm.nih.gov/pmc/articles/PMC2974327/#:~:text=Observational%20studies%20have%20generally%20found,birth%20weight%20or%20infant%20adiposity.&text=Moreover%2C%20maternal%20adiposity%20tends%20to,BMI29%20than%20paternal%20adiposity.) of infant birthweight
* fincome may be predictive of access to resources (esp during pregnancy), including medical care, adequate nutrition, etc. 
* parity [is a signficiant predictor](https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3922415/#:~:text=Maternal%20parity%20is%20a%20well,infants%20born%20to%20nulliparous%20women.) of birthweight
* baby head is also predictive of bw based on what I remember from my Global Health nutrition case studies


Some exploration to visualize chosen vars (replaced different x vars using this same structure)
```{r}
birthweight_df %>% 
  ggplot(aes(x = gaweeks, y = bwt)) +
  geom_point() +
  labs(
    x = "gestational age in weeks",
    y = "birthweight",
    title = "Visualization Model"
  )
```


let's try fitting a model
```{r}
bw_model_1 = lm(bwt ~ delwt + blength + gaweeks + mrace + smoken + babysex + ppbmi + fincome + parity + bhead, data = birthweight_df)
```

and visualize it:
```{r}
bw_model_1 %>% 
  broom::tidy() %>% 
summary(bw_model_1)
coef(bw_model_1)
```

This shows us that maternal weight, infant length, gestational age, male sex, smoking, pre-pregnancy BMI, family income, parity, and Black race are all signficantly associated with infant birthweight. 

I considered but ultimately didn't include several factors based on the fact that they were not significantly associated with infant birthweight based on the summary of my model. I combined background info/research with a little bit of trial and error to come up with this model. Unclear as to whether this model is truly optimal. 

Plotting this model:
```{r}
birthweight_df %>% 
modelr::add_residuals(bw_model_1) %>% 
  add_predictions(bw_model_1, var = "pred", type = NULL) %>% 
  add_residuals(model = bw_model_1, var = "resid") %>% 
  ggplot(aes(x = pred, y = resid)) +
  geom_point(alpha = 0.3) +
  labs(
    x = "fitted values",
    y = "residuals",
    title = "Residuals against fitted values"
  )
  

```


Now, compare to model using length at birth and gestational age as predictors
```{r}
bw_model_2 = lm(bwt ~ blength + gaweeks, data = birthweight_df)
```

And compare to model using head circumference, length, sex, and all interactions (including 3-way interaction) between

```{r}
bw_model_3 = lm(bwt ~ bhead + blength + babysex + bhead*blength*babysex, data = birthweight_df)
```

And now to cross-validate
```{r}
cv_df = 
  crossv_mc(birthweight_df, 100)

cv_df2 = 
  cv_df %>% 
  mutate(
    bw_model_1 = map(.x = train, ~lm(bwt ~ delwt + blength + gaweeks + mrace + smoken + babysex + ppbmi + fincome + parity, data = .x)),
    bw_model_2 = map(.x = train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    bw_model_3 = map(.x = train, ~lm(bwt ~ bhead + blength + babysex + bhead*blength*babysex, data = .x))
    ) %>% 
   mutate(
    rmse_model1 = map2_dbl(.x = bw_model_1, .y = test, ~rmse(model = .x, data = .y)),
    rmse_model2 = map2_dbl(.x = bw_model_2, .y = test, ~rmse(model = .x, data = .y)),
    rmse_model3 = map2_dbl(.x = bw_model_3, .y = test, ~rmse(model = .x, data = .y))
  )

cv_df2 %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_"
  ) %>% 
  ggplot(aes(x = model, y = rmse)) +
  geom_violin() + 
  labs(
    x = "model",
    y = "rmse",
    title = "rmse values for models 1 to 3 (L to R)"
  )


```

Based on this figure, it would appear that model 3 has the lowest median RMSE value, while model 2 has the highest. 


## Problem 3

download dataset, fit model to dataset, make sure can compute adjusted r-sq (comes from broom::glance), broom::tidy, estimated coefficients, rearrange things so have intercept and slope next to each other that you can multiply and take the log of. 

Import dataset
```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything()) 
  
```

Bootstrap - find r-squared
```{r}
r_sq_boot = 
weather_df %>% 
  bootstrap(5000, id = "strap_number") %>% 
  mutate(
  models = map(.x = strap, ~lm(tmax ~ tmin, data = .x)),
  results = map(models, broom::glance)
  ) %>% 
  unnest(results) %>% 
  select(r.squared)
```

Display distribution of r-sq values
```{r}
r_sq_boot %>% 
  ggplot(aes(x = r.squared)) + 
  geom_density() +
  labs(
    x = "r-squared values",
    title = "Distribution of r-squared values"
  )
```

The r-squared values appear to be normally distributed with a slight left skew and a median value around 0.913.

Now, onto finding log(β̂ 0∗β̂ 1)
```{r}
log_boot =
  weather_df %>% 
  bootstrap(5000, id = "strap_number") %>% 
  mutate(
  models = map(.x = strap, ~lm(tmax ~ tmin, data = .x)),
  results = map(models, broom::tidy)
  ) %>% 
  select(strap_number, results) %>% 
  unnest(results)
```

manipulate these results to find the log
```{r}
log_boot_results = 
log_boot %>% 
  unnest() %>% 
  select(term, estimate) %>% 
  pivot_wider(
    names_from = "term",
    values_from = "estimate"
  ) %>% 
  unnest() %>% 
  rename(
    intercept = "(Intercept)"
  ) %>% 
  mutate(
    log_est = log(intercept*tmin)
  )

log_boot_results
# I tried to do this first with tmin~tmax, but it produced negative values only, which meant that my log function wouldn't work. Switched it around and it finally worked. 
```

plot the log distribution
```{r}
log_boot_results %>% 
  ggplot(aes(x = log_est)) + 
  geom_density() +
  labs(
    x = "logB0*B1 values",
    title = "Distribution of logB0*B1 values"
  )
```

These log values appear to be fairly normally and symmetrically distributed, with a median around 2.02. 


Let's find confidence intervals
```{r}
# CI for log estimates

CI_log = 
log_boot_results %>% 
  summarize(
    ci_lower = quantile(log_est, 0.025),
    ci_upper = quantile(log_est, 0.975)
  ) %>% 
  knitr::kable()

CI_log

CI_rsq = 
  r_sq_boot %>% 
  summarize(
       ci_lower = quantile(r.squared, 0.025),
    ci_upper = quantile(r.squared, 0.975)
  ) %>% 
  knitr::kable()


CI_rsq

```


* The 95% CI for log(β̂ 0∗β̂ 1) is (1.965118, 2.05854).
* The 95% CI for r squared is (0.8943899, 0.9269525).
